Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-23 paper/paper.tex
Finish 10th page

Description, on the other hand, even though it is made to be a more detailed summary of the report, it should still be
in some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
with more than 4,000 words. Even though they included various types of information, including steps to reprodce, 
we believe that the reason why Jira and the other popular issue tracking systems created so many fields for bug reports 
is that the information that could all be put in description should be split across these fields: 
\begin{itemize}
  \item if there are stack traces or steps to reproduce, as we mentioned above, there should be specific fields 
  created exclusively for them; 
  \item if the end user is an experienced one and has reported numerous bugs or feature requests for the project, 
  they might also be able to provide an estimate for the difficulty of the task; however, that should be stored in the 
  Jira system field called \"Story Points\";
  \item the user might also want to provide excerpts of code or previous discussions with other end users/developers; 
  however, they should not upload it inside the description field, but rather create a text attachment (e.g. markdown
  document) and attach it separately so that they keep the description clean and easy to follow.
\end{itemize}

A solution for this issue could be the freedom of easily selecting the total number of words allowed for summary and 
description. Even though this is possible with Jira, the process of configuring it is not trivial, thus many 
administrators do not perform this step. An even better approach would be to have a tool automatically generating 
word limits based on, for example, the experience of the reporter - if he/she has significant knowledge regarding 
the project, they should be allowed to include lengthier summaries or descriptions mainly because they are more inclined 
to know that without a very good reason, following this approach is not the most optimal way.

@@

Through calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
managed to calculate the total number of grammar errors in summary, description and comments for a total number 
of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
However, in the work conducted by Schugerl et al. \cite{schugerl2008mining}, the authors found that spelling errors 
can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
the Time-To-Close for a ticket. In the rest of this section we will demonstrate the contrary - tickets with more 
grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
tickets (i.e. increased \emph{Time-To-Close}).

This analysis type is called grammar correctness rather than spelling scores because the range of errors returned 
by Bing Spell Check API are of many types, some of which are:
\begin{itemize}
  \item spelling errors; however, they go much further than a simple character mistyped - for example,
  if one would type Micrsft, it would automatically flag it as a grammar error because it also takes into account a large 
  database of words not in standard dictionaries, but also popular words in the tech world (e.g. company names) or 
  jargon language (e.g. dab dance);
  \item contextual errors - e.g. I ate a book today; even though this is not a misspell, the API will return \emph{book} as 
  a grammar error due to the fact that it is used in the wrong context;
  \item it can detect the wrong usage of a verb tense in a specific context;
  \item it can flag wrong conjugations of verbs;
\end{itemize}

@@

However, we can not automatically change this through automation like the solutions we presented in the previous 
analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
is inputting in the ticket as the costs would become unbearable very soon. Thus, what can be done to fix this? It is, 
after all, in the human nature to make mistakes, and typing is no exception. If we, for example, have some hint or a rule
in the code of conduct for the project stating that everything should be 100\% gramatically correct, many reporters not 
having English as their primary language would feel unwelcomed and they might not get involved in the project anymore.

>>>>

Description, on the other hand, even though it is made to be a more detailed summary of the report, it should still be
within some reasonable parameters. During our analysis process, we identified more than 50 tickets having descriptions 
with more than 4,000 words. Even though they included various types of information, including steps to reprodce, 
we believe that the reason why Jira and the other popular issue tracking systems created so many fields for bug reports 
is that the information that could all be put in description should be split across these fields: 
\begin{itemize}
  \item if there are stack traces or steps to reproduce, as we mentioned above, there should be specific fields 
  created exclusively for them; 
  \item if the end user is an experienced one and has reported numerous bugs or feature requests for the project, 
  they might also be able to provide an estimate for the difficulty of the task; however, that should be stored in the 
  Jira system field called Story Points;
  \item the user might also want to provide excerpts of code or previous discussions with other end users/developers; 
  however, they should not upload it inside the description field, but rather create a text attachment (e.g. markdown
  document) and attach it separately so that they keep the description clean and easy to follow.
\end{itemize}

A solution for this issue could be a setting to cap the total number of words allowed for summary and 
description. Even though this is possible with Jira, the process of configuring it is not trivial, thus many 
administrators do not perform this step. An even better approach would be to have a tool automatically generating 
word limits based on, for example, the experience of the reporter - if he/she has significant knowledge regarding 
the project, they should be allowed to include lengthier summaries or descriptions mainly because they are more inclined 
to know that without a very good reason, following this approach is not the most optimal way.

@@

By calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
managed to calculate the total number of grammar errors in summary, description and comments for a total number 
of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
However, in the work conducted by Schugerl et al. \cite{schugerl2008mining}, the authors found that spelling errors 
can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
the Time-To-Close for a ticket. In the rest of this section we will demonstrate the contrary - tickets with more 
grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
tickets (i.e. increased \emph{Time-To-Close}).

This analysis type is called grammar correctness rather than spelling scores because the range of errors returned 
by Bing Spell Check API are of many types, some of which are:
\begin{itemize}
  \item spelling errors; however, they go much further than a simple character mistyped - for example,
  if one would type Micrsft, it would automatically flag it as a grammar error because it also takes into account a large 
  database of words not in standard dictionaries, but also popular words in the tech world (e.g. company names) or 
  jargon language (e.g. dab dance);
  \item contextual errors - e.g. I ate a book today; even though this is not a misspell, the API will return \emph{book} as 
  a grammar error due to the fact that it is used in the wrong context;
  \item it can detect the wrong usage of a verb tense in a specific context;
  \item it can flag wrong conjugations of verbs.
\end{itemize}

@@

However, we can not change this through automation like the solutions we presented in the previous 
analysis types. We cannot call, for example, the Bing Spell Check API every couple of seconds on the text the user 
is inputting in the ticket as the costs would become unbearable very rapidly. Thus, what can be done to fix this? It is, 
after all, in the human nature to make mistakes, and mistyping is no exception. If we, for example, have some hint or a rule
in the code of conduct for the project stating that everything should be 100\% gramatically correct, many reporters with a 
different language than English as their primary one would feel unwelcome and they might not get involved in the project anymore.
